Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-04-22 analysis/paper/paper.Rmd
fix conflict

```{r tidy-data}
# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

@@

```{r read-in-the-spatial-data}
library(sf)
library(cartography)
burial <- st_read(here("analysis", "data", "raw_data", "AD_burial.shp"))
AD <- st_read(here("analysis", "data", "raw_data", "AD_zone.shp"))
AD_data <- st_read(here("analysis", "data", "raw_data", "AD_withdata.shp"))
location <- st_read(here("analysis", "data", "raw_data", "location.shp"))
units_40 <- read.csv(here("analysis", "data", "raw_data", "kwl-list-of-sampling-squares.csv"))
```

```{r tidy-data2}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))

>>>>

```{r tidy-data, eval = TRUE}

# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

@@

```{r read-in-the-spatial-data, eval = TRUE}

library(sf)
library(cartography)
burial <- st_read(here("analysis", "data", "raw_data", "AD_burial.shp"))
AD <- st_read(here("analysis", "data", "raw_data", "AD_zone.shp"))
AD_data <- st_read(here("analysis", "data", "raw_data", "AD_withdata.shp"))
location <- st_read(here("analysis", "data", "raw_data", "location.shp"))
units_40 <- read.csv(here("analysis", "data", "raw_data", "kwl-list-of-sampling-squares.csv"))
```

```{r tidy-data2, eval = TRUE}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))
